InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
Reduce whitespace between figures
Replace enumeration by text

This is done in two steps:

\begin{enumerate}
	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
\end{enumerate}

@@

We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.

\cite{radford2019language} try to avoid this problem in a simple two step procedure:

\begin{enumerate}
	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
	\item Discriminative fine-tuning on every specific task.
\end{enumerate}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{images/stable-diffusion.png}
	\caption{Stable Diffusion with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
	\label{fig:stable_diffusion}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{images/dalle.png}
	\caption{Dall-E with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
	\label{fig:dallE}
\end{figure}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{images/gpt2.png}
	\caption{GPT2 with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
	\label{fig:gpt2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{images/falcon.png}
	\caption{Falcon with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
	\label{fig:falcon}
\end{figure}

>>>>

This is done in two steps: Firstly, The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer. Secondly, BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.

@@

We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.\cite{radford2019language} try to avoid this problem in a simple two step procedure: Firstly, a generative pre-training of a language model on a varying corpus of unlabeled text. Secondly, discriminative fine-tuning on every specific task.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{images/stable-diffusion.png}
	\caption{Stable Diffusion with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
	\label{fig:stable_diffusion}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{images/dalle.png}
	\caption{Dall-E with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
	\label{fig:dallE}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{images/gpt2.png}
	\caption{GPT2 with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
	\label{fig:gpt2}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{images/falcon.png}
	\caption{Falcon with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
	\label{fig:falcon}
\end{figure}
